\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
put in rough screentime stats

%how much time participants in aggregate spent in progress bar 
overall, participants spent 65\% of their time in the progress bar. 
e1 participants spent 28\% of their time in the progress bar. 
e2 participants spent 74\% of their time in the progress bar. 
e3 participants spent 63\% of their time in the progress bar. 
new participants spent 78\% of their time in the progress bar. 
old participants spent 57 \% of their time in the progress bar.

% how much time participants spent on average would be nice. (maybe I can do this later). 
%	i.e. the average participant in e1 spent x\% of their time in the progress bar.

% overall time spent configuring a proxy
overall, participants spent 18\% of their overall time configuring a proxy. 
e1 participants spent 16\% of their overall time configuring a proxy. 
e2 participants spent 10\% of their overall time configuring a proxy. 
e3 participants spent 21\% of their overall time configuring a proxy.  
new participants spent 7\% of their overall time configuring a proxy.  
old participants spent 25 \% of their overall time configuring a proxy.

% ``active'' time spent configuring a proxy
overall, participants spent 52\% of their active time configuring a proxy. 
e1 participants spent 22\% of their active time configuring a proxy. 
e2 participants spent 40\% of their active time configuring a proxy. 
e3 participants spent 57\% of their active time configuring a proxy.  
new participants spent 31\% of their active time configuring a proxy.  
old participants spent 58\% of their active time configuring a proxy.

% how much time participants spent on average during their ``active time'' would be nice (maybe I can do this later). 
% 	i.e. the average participant in new spent x\% of their active time configuring a proxy.

@@

@@

% basic statistics (BAD, NEED CHI SQUARED NOT KRUSKAL AND EXCLUDED DNFs)
%Results from statistical analyses say: 
%\begin{itemize} 
%	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
%	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
%	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
%	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
%	\item{{\bfseries impact of configuration version on success rate is not significant.}
%	Mann-Whitney, W = 5.5, p-value = 0.8248}
%	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
%	Mann-Whitney, W = 991, p-value = 0.3197}
%\end{itemize}

% looking at all factors' impact on success rate (SUCCESS RATHER THAN SUCCESS RATE?)
%A logistic regression model showing effects of censorship environment, interface version,
%and recruitment pool on success finds that a difficult censorship environment is the most
%significant factor in a participant failing. Xlab participants were more likely to succeed. 
%Participants with the old version of the interface were more likely to fail. 
%
%Coefficients:
%             Estimate Std. Error z value Pr(>|z|)  
%(Intercept)   19.4556  1684.3342   0.012   0.9908  
%envE2        -17.3458  1684.3342  -0.010   0.9918  
%envE3        -19.2652  1684.3341  -0.011   0.9909  
%versionOLD    -0.7095     0.5793  -1.225   0.2206  
%poolxlab       1.1218     0.5968   1.880   0.0601 .
%---
%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

% looking at all factors' impact on time to completion (BAD, EXCLUDED DNFs)
%A linear regression model showing effects of censorship environment, interface version, 
%and recruitment pool on success finds that a difficult censorship environment is the most
%significant factor in taking a long time to complete the task. Participants with the old version
%of the interface and participants recruited from Xlab were likely to take longer. 
%
%Coefficients:
%            Estimate Std. Error t value Pr(>|t|)    
%(Intercept)   -42.79      86.70  -0.494  0.62280    
%envE2         300.65      90.13   3.336  0.00124 ** 
%envE3         923.66     100.94   9.150 1.68e-14 ***
%versionOLD    104.78      78.70   1.331  0.18642    
%poolxlab       92.41      78.88   1.172  0.24445    
%---
%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

>>>>

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\end{table}

@@

% new people still spent time configuring their proxy!

@@
